Complete Real-Time Liver Model including Glisson Capsule, Vascular Network and Parenchyma

### 2013-03-01 Doc/Miccai2013/miccai2013.tex
ADD: part of the global deformation section plus images
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@543 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\usepackage{amsmath}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}

@@

\begin{figure}[htb]
  \centering
    \includegraphics[width=.25\textwidth]{gravity.jpg}
  \caption{\label{fig-gravity}Vascularized liver under pure gravity with (red) and without (green) the capsule.}
\end{figure}

>>>>

\usepackage{amsmath}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}
\usepackage{subfigure}

@@

\begin{figure}[htb]
  \centering
    \subfigure[]{\includegraphics[width=.32\textwidth]{gravity2.png}}
    \subfigure[]{\includegraphics[width=.32\textwidth]{registered.png}}
    \subfigure[]{\includegraphics[width=.32\textwidth]{distanceMap.png}}
  \caption{\label{fig-gravity}Vascularized liver under pure gravity with (red) and without (green) the capsule.}
\end{figure}

In the previous section we have shown that the composite model of parenchyma and 
capsule can be used to reproduce the \emph{local} behaviour of the tissue. In the following, 
first we present a real-time complete model of entire liver built from image data. 
Second, using this model we demonstrate the \emph{global} mechanical influence of the capsule when 
the model undergoes large deformations.

The complete model was constructed using constrast-enhanced CT data acquired on a female pig 
being positioned first in supine and then flank configuration. 
The liver and hepatic vein were segmented for both datasets  using semi-automatic methods available in ITKSnap.
Further, an unstructured mesh was obtained from the segmented maps using algorithm~\cite{boltcheva}
available in ITKSnap. The semiautomatic method presented in~\cite{peterlik2012} was 
then applied to the segmented map of the hepatic vein, resulting in linked-beam model. 
Finally, the model of the Glisson's capsule was constructed using the elements described in 
section~\ref{} over the surface triangles extracted from the tetrahedral mesh. 
The complete model composed of 6200 tetrahedra, 220 beams and 1820 triangles was then 
used in simulation where external force representing the gravity was applied to the model, 
resulting in large deformations mainly in the area of lobes. The refresh rate of 10\,FPS 
was achieved on a desktop computer with Intel i7 CPU running at 3\,GHz and 16\,GB of memory.
